---
title: "GPT detection models"
date: 2023-07-25
output: html_document
---

# Overview

In this study the authors evaluated the performance of various AI GPT detectors by passing written essays by native and non-native English writers to different **GPT detection models**. The authors argue that **GPT detection models** disproportionately classify real writing from non-native English writers as AI generated.

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(tidytuesdayR)

```

# Load the weekly Data

Download the weekly data and make available in the `tt` object.

```{r Load}

tt <- tt_load("2023-07-18")

```

# Readme

The detectors dataset is from an R package named detectors, to install the package:

```{r}
require(pak)
pak::pak("simonpcouch/detectors")
```

```{r Readme, eval = interactive()}

tt

```

# Glimpse Data

The data is composed of 9 variables containing the type of detectors used to generate the predictions (**detector**) and the prediction whether is AI producing the text or not (**.pred_class**). A variable with the specification of the type of model used to generate the essay is also included (**model**).

```{r Glimpse}

tt %>% 
  map(glimpse)

```
Store in detector variable and change (**kind**) and (**.pred_class**) column to factors.

```{r}
detectors <- tt$detectors
dtrs <- detectors %>%
  mutate_at(c('kind','.pred_class'),as.factor)


```

Exploration

```{r}

dtrs %>%
  count(native, kind, .pred_class)

# Native speakers are more likely to be detected as human while non-native are more like to be misclassified.
dtrs %>%
  filter(!is.na(native)) %>%
  mutate(native = case_when(native == "Yes" ~ "Native English Writer",
                            native == "No" ~ "Non-Native English Writer")) %>%
  ggplot(aes(.pred_AI, fill = native)) +
  geom_histogram(show.legend = FALSE) +
  facet_wrap(vars(native), scales = "free_y", ncol = 1)

```

```{r}
library(yardstick)
dtrs %>%
  conf_mat(kind, .pred_class)

```
```{r}
dtrs %>%
  accuracy(kind, .pred_class)
```


```{r}
dtrs %>%
  group_by(detector) %>%
  accuracy(kind, .pred_class)
```


```{r}
dtrs %>%
  group_by(native) %>%
  accuracy(kind, .pred_class)
```


```{r}
dtrs %>%
  group_by(detector) %>%
  sensitivity(kind, .pred_class)
```


```{r}
dtrs %>%
  filter(!is.na(native)) %>%
  conf_mat(kind, .pred_class)
```

# Visualize

Using your processed dataset, create your unique visualization.

```{r Visualize}

dtrs %>%
  group_by(detector) %>%
  roc_curve(kind, .pred_AI) %>%
  autoplot()
  
```
```{r}

dtrs %>%
  group_by(detector) %>%
  roc_curve(kind, .pred_AI)

```
```{r}
dtrs %>%
  group_by(native) %>%
  mn_log_loss(kind, .pred_AI)
```

